%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


\newcommand{\zap}[1]{ }

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{black}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75, top=2cm, bottom=2.54cm]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{enumerate}

\usepackage{fontspec}

\usepackage{color}

\setmainfont[Ligatures=TeX]{Times New Roman}

\renewcommand*{\cventry}[7][1em]{
  \begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}%
    {#3} & {\small\itshape#2}\\%
    {#4} & \\
    {#6} & \\
   %
  \end{tabular*}%
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      #7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\renewcommand*{\cvitemwithcomment}[4][1em]{%
  \savebox{\cvitemwithcommentmainbox}{\ifthenelse{\equal{#2}{}}{}{\hintstyle{#2}: }#3}%
  \setlength{\cvitemwithcommentmainlength}{\widthof{\usebox{\cvitemwithcommentmainbox}}}%
  \setlength{\cvitemwithcommentcommentlength}{\maincolumnwidth-\separatorcolumnwidth-\cvitemwithcommentmainlength}%
  \begin{minipage}[t]{\cvitemwithcommentmainlength}\usebox{\cvitemwithcommentmainbox}\end{minipage}%
  \hfill% fill of \separatorcolumnwidth
  \begin{minipage}[t]{\cvitemwithcommentcommentlength}\raggedleft\small\itshape #4\end{minipage}%
  \par\addvspace{#1}}

\renewcommand*{\makecvhead}{% TODO: use \@initializecommand, which requires modifying its definition to handle \par
  % recompute lengths (in case we are switching from letter to resume, or vice versa)
%  \recomputecvlengths%
  \makehead%
  }% to avoid weird spacing bug at the first section if no blank line is left after \maketitle}

\newcommand{\cvexpr}[5][1em]{
  \begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}%
    {\textbf{#3}\ifthenelse{\equal{#4}{}}{}{, #4}} & {\small\itshape#2}%
  \end{tabular*}%
  \\
  \begin{minipage}{\maincolumnwidth}%
        #5%
  \end{minipage}%
  \par\addvspace{#1}
}

% personal data
\name{Chen}{Luo}
\address{Department of Computer Science, University of California, Irvine}{Irvine}{CA}
\mobile{949-372-8206}                         
\email{cluo8@uci.edu}
%\homepage{luochen01.github.io}


\begin{document}
\makecvtitle

\section{Education}

\cventry{Sept. 2016--Present}{\textbf{University of California, Irvine}, CA}{Ph.D. in Computer 
Science }{}{Supervisor: Prof. Michael Carey}{}

\cventry{Sept. 2013--July 2016}{\textbf{Tsinghua University}, China}{M.Eng. in Software 
Engineering}{}{GPA: 94.1/100, Ranking: 2 out of 136}{
Thesis: Policy-Based Privacy Checking for Big Data Analytics Systems
}
\cventry{Sept. 2009--July 2013}{\textbf{Tongji University}, China}{B.Eng. in Software Engineering}{}{GPA: 4.72/5, Ranking: 2 out of 169}{
Thesis: Design and Implementation of a Distributed Key-Value Storage System
}



\section{Research Experience}

\cvexpr{Aug. 2015--May 2016}{Logic-based Enforcement of SQL Data Use Policies}{Tsinghua 
University}{
 \begin{itemize}
  \item Proposed a logic-based approach for enforcing SQL data use policies
  \item Defined a novel specification logic combining LTL and CTL for SQL query sequences
  \item Implemented the approach on top of Spark-SQL, and demonstrated practicality with a case 
  study comprising 106 real world policies
 \end{itemize}
}

\cvexpr{July 2014--Dec. 2015}{PSpec-SQL}{Tsinghua University}{
\begin{itemize}
\item Tsinghua--Intel Joint Research Project
\item Built a privacy-integrated data analytics system on top of Spark-SQL, which:
	\begin{itemize}
		\item Provides a high-level privacy language for specifying privacy policies
		\item Enforces privacy compliances against submitted queries using program analysis techniques
		\item Integrates with differential privacy to offer provable privacy guarantees
	\end{itemize}
\end{itemize}
}

\cvexpr{Mar. 2014--July 2014}{Large-Scale Software Model Inference}{Tsinghua University}{
\begin{itemize}
\item Independent Research Project
\item Proposed a MapReduce-based approach for inferring software models from large logs
\item Demonstrated efficiency and scalability with extensive experiments on AWS cloud
\end{itemize}

}

\zap{
\cvexpr{Sept. 2013--Dec. 2013}{DQCup}{Tsinghua University}{
\begin{itemize}
\item Course Project for \textit{Advanced Topics in Data Quality}
\item Developed a data cleaning tool integrating various data cleaning techniques for a given task
\item Ranked 1st among 15 teams in terms of detection accuracy, repairing accuracy, and performance
\end{itemize}
}
}

\cvexpr{Dec. 2012--June 2013}{KVStore}{Tongji University}{
\begin{itemize}
\item Bachelor Thesis Project
\item Built a distributed key-value storage system with in-memory/persistent engines
\item Key features include fault tolerance and automatic load balancing
\end{itemize}
}

\section{Publications}
\begin{enumerate}[{[1]}]
\item \cvitem{}{\textbf{Chen Luo}, Fei He, and Carlo Ghezzi. Inferring Software Behavioral Models 
with MapReduce. \textit{International Symposium on Dependable Software 
Engineering: Theories, Tools and Applications (SETTA)}, November 2015
}

\item \cvitem{}{\textbf{Chen Luo}, Fei He, Dong Yan, Dan Zhang, Xin Zhou, and Bow-Yaw 
  Wang. PSpec: A Formal Privacy Language for Data Analytics (Poster). \textit{International 
  Conference on Software Engineering (ICSE)}, May 2017. \textit{To appear}
}

\item \cvitem{}{\textbf{Chen Luo}, Fei He. SMT-Based Query Tracking for Differentially Private Data 
  Analytics Systems. \textit{Frontiers of Computer Science}. \textit{To appear}}

\item \cvitem{}{\textbf{Chen Luo}, Fei He, Fei Peng, Dong Yan, Dan Zhang, and Xin Zhou. PSpec-SQL: 
Enforcing Privacy Policies in Big Data Analytics. \textit{Under Submission}
}

\item \cvitem{}{Ning Liu, \textbf{Chen Luo}, Fei He. A Logical Approach to
  Enforcing SQL Data Use Policies. \textit{Under Submission}}

\end{enumerate}

\section{Presentation}
\cvlistitem{Inferring Software Behavioral Models with MapReduce. \textit{International Symposium on 
Dependable Software Engineering: Theories, Tools and Applications (SETTA)}, Nanjing, China, 
November 2015}


\section{Work Experience}
\cvexpr{Mar. 2014--May 2016 }{Research Assistant}{Tsinghua University}{
  \cvlistitem{Led a group in conducting research on security and privacy aspects of data analytics 
    systems}
  \cvlistitem{Conducted independent research on formal methods}
}

\cvexpr{July 2012--Mar. 2013}{Software Developer Intern}{eBay China Development Center}{
  \cvlistitem{Participated in the development of eBay's web application framework}
  \cvlistitem{Redeveloped the internal web traffic analytics system with MapReduce}
}

\cvexpr{Mar. 2011--June 2012}{Research Assistant}{Tongji University}{
  \cvlistitem{Participated in the development of a customer service and support system}
}

\section{Teaching Assistant}
\cvlistitem{\cvitemwithcomment{}{Programming in C++ as a Second Language, University of California, 
Irvine}{Fall 2016}}

\cvlistitem{\cvitemwithcomment{}{Modeling and Verification of Software Systems, Tsinghua 
University}{Spring 2015}}

\cvlistitem{\cvitemwithcomment{}{Object-Oriented Programming C++, Tongji University}{Spring 2011}}


\section{Honors \& Awards}
\cvlistitem{\cvitemwithcomment{}{Graduate with Honor of Beijing, Tsinghua University (top 
    5\%)}{2016}}
\cvlistitem{\cvitemwithcomment{}{First Class Scholarship, Tsinghua University (top 10\%)}{2014, 
2015}}
\cvlistitem{\cvitemwithcomment{}{Graduate with Honor of Shanghai, Tongji University (top 
5\%)}{2013}}
\cvlistitem{\cvitemwithcomment{}{Outstanding Student, Tongji University (top 5\%)}{2010, 2011}}
\cvlistitem{\cvitemwithcomment{}{First Class Scholarship, Tongji University (top 5\%)}{2011}}


\section{Technical Skills}
\cvlistitem{\textbf{Programming Languages}: Java, C/C++, Scala, Python, SQL, R, Bash}
\cvlistitem{\textbf{Databases and Systems}: MySQL, Hadoop, Spark, Spark-SQL, Hive}
\cvlistitem{\textbf{Software Tools}: Eclipse, LaTex, Visual Studio, Matlab}

\clearpage
\end{document}
