%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\newcommand{\zap}[1]{ }
\newcommand{\reduce}{\vspace{-0.115in}}

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{black}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75, top=1.4cm, bottom=1.4cm]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{enumerate}

\usepackage{fontspec}
\usepackage{fontawesome}

\usepackage{color}

\setmainfont[Ligatures=TeX]{Times New Roman}

\renewcommand*{\cventry}[7][1em]{
  \begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}%
    {#3} & {\small\itshape#2}\\%
    {#4} &  \\
    {#6} & \\
   %
  \end{tabular*}%
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      #7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\cvschool}[6][1em]{
	\begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}%
		{#3} & {\small\itshape#2}\\%
		{#4} & {\small #5} \\
		%
	\end{tabular*}%
	\ifx&#6&%
	\else{\\%
		\begin{minipage}{\maincolumnwidth}%
			#6%
	\end{minipage}}\fi%
	\par\addvspace{#1}}

\renewcommand*{\cvitemwithcomment}[4][1em]{%
  \savebox{\cvitemwithcommentmainbox}{\ifthenelse{\equal{#2}{}}{}{\hintstyle{#2}: }#3}%
  \setlength{\cvitemwithcommentmainlength}{\widthof{\usebox{\cvitemwithcommentmainbox}}}%
  \setlength{\cvitemwithcommentcommentlength}{\maincolumnwidth-\separatorcolumnwidth-\cvitemwithcommentmainlength}%
  \begin{minipage}[t]{\cvitemwithcommentmainlength}\usebox{\cvitemwithcommentmainbox}\end{minipage}%
  \hfill% fill of \separatorcolumnwidth
  \begin{minipage}[t]{\cvitemwithcommentcommentlength}\raggedleft\small\itshape #4\end{minipage}%
  \par\addvspace{#1}}

\renewcommand*{\makecvhead}{% TODO: use \@initializecommand, which requires modifying its definition to handle \par
  % recompute lengths (in case we are switching from letter to resume, or vice versa)
%  \recomputecvlengths%
  \makehead%
  }% to avoid weird spacing bug at the first section if no blank line is left after \maketitle}


\newcommand{\cvexpr}[5][1em]{
  \begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}%
    {\textbf{#3}\ifthenelse{\equal{#3}{}}{\textbf{#4}}{, #4}} & {\itshape#2}%
  \end{tabular*}%
  \\
  \begin{minipage}{\maincolumnwidth}%
        #5%
  \end{minipage}%
  \par\addvspace{#1}
}

% personal data
\name{Chen}{Luo}
\address{Department of Computer Science, University of California, Irvine}{Irvine}{CA}
\mobile{949-372-8206}                         
\email{cluo8@uci.edu}


\begin{document}
\makecvtitle

\reduce
\section{Research Interest}
\vspace{-0.05in}
Database Storage Management, LSM-trees, Indexing

\reduce
\section{Education}
\vspace{-0.05in}
\cvschool{Sept. 2016--Dec. 2020}{\textbf{University of California, Irvine}, CA}{Ph.D. in Computer Science. Supervisor: Michael J. Carey}{GPA: 4.00/4.00}
{Thesis: On Optimizing LSM-based Storage for Big Data Management Systems}
\vspace{-0.15in}
\cvschool{Sept. 2013--July 2016}{\textbf{Tsinghua University}, China}{M.Eng. in Software 
Engineering}{GPA: 94.1/100 (2 out of 136)}{}
\vspace{-0.15in}
\cvschool{Sept. 2009--July 2013}{\textbf{Tongji University}, China}{B.Eng. in Software Engineering}{GPA: 4.72/5 (2 out of 169)}{}

\reduce
\reduce


\section{Research Experience}
\vspace{-0.05in}
\cvexpr{}{}{Efficient Maintenance and Exploitation of LSM-based auxiliary structures [PVLDB'19]}{
\begin{itemize}
	\item Designed various primary lookup optimizations exploiting LSM-tree's multi-components design
	\item Proposed a Validation strategy to maintain LSM-based secondary indexes lazily and more efficiently
	\item Proposed a Delete-Bitmap strategy to maximize the pruning capabilities of LSM-based filters
\end{itemize}
}
\reduce
\cvexpr{}{}{Minimizing LSM-tree's Write Stalls via Novel Merge Scheduling [PVLDB'20]}{
	\begin{itemize}
		\item Proposed a two-phase evaluation approach to evaluate write stalls of various LSM-tree designs
		\item Proposed a novel greedy merge scheduler to minimize write stalls of LSM-trees
		\item Substantially reduced percentile write latencies without impacting write throughput
	\end{itemize}
}
\reduce
\cvexpr{}{}{Adaptive Memory Management of LSM-trees [Under Submission]}{
	\begin{itemize}
		\item Proposed a memory management architecture to enable adaptive memory management for LSM-trees
		\item Proposed a new memory component structure to better exploit large memory to minimize write costs
		\item Designed and implemented a memory tuner to tune optimal memory allocation between write memory and buffer cache
	\end{itemize}
}

\reduce
\reduce

\section{Internship Experience}
\cvexpr{June 2019--Sep. 2019}{Research Intern}{Microsoft Research, Redmond}{
	\begin{itemize}
		\item Mentor: David Lomet
		\item Built a customized SSD controller on open-channel SSDs while supporting variable-size pages
	\end{itemize}
}
\reduce
\cvexpr{June 2017--Sep. 2017}{Research Intern}{IBM Almaden Research Center}{
	\begin{itemize}
		\item Mentor: Pinar Tozun, Yuanyuan Tian
		\item Designed and implemented a multi-zone indexing method for HTAP systems that provides a unified view for evolving data [EDBT'19]
	\end{itemize}
}
\reduce
\cvexpr{July 2012--Mar. 2013}{Software Developer Intern}{eBay China Development Center}{
\begin{itemize}
	\item Participated in the development of eBay's web application framework
	\item Redeveloped the internal web traffic analytics system with MapReduce
\end{itemize}
}
\reduce

\section{Selected Publications}
\vspace{-0.05in}
\begin{enumerate}[{[1]}]
\item \cvitem{}{\textbf{Chen Luo}, Michael J. Carey. LSM-based storage techniques: a survey. \emph{VLDB Journal}, 29 (1), pp. 393--418, 2020}
\reduce
\item \cvitem{}{\textbf{Chen Luo}, Michael J. Carey. Efficient data ingestion and query processing for LSM-based storage systems. \emph{PVLDB}, 12(5), pp. 531--543, 2019}
\reduce
\item \cvitem{}{\textbf{Chen Luo}, Michael J. Carey. On performance stability in LSM-based storage systems. \emph{PVLDB}, 13(4), pp. 449--462, 2019}
\reduce
\item \cvitem{}{\textbf{Chen Luo}, Pinar Tozun, Yuanyuan Tian, Ronald Barber, Vijayshankar Raman, and Richard Sidle.
Umzi: Unified Multi-Zone Indexing for Large-scale HTAP. \emph{EDBT}, pp. 1--12, 2019}
\reduce
\item \cvitem{}{\textbf{Chen Luo}, Michael J. Carey. Breaking down memory walls: adaptive memory management for LSM-based storage systems. \emph{Under submission}}
\end{enumerate}

\zap{
\reduce
\item \cvitem{}{\textbf{Chen Luo}, Fei He, Dong Yan, Dan Zhang, Xin Zhou, and Bow-Yaw 
	Wang. PSpec-SQL: Enabling Fine-Grained Control for Distributed Data Analytics. \textit{IEEE Transactions on Dependable and Secure Computing (TDSC)}, 2019
}
\reduce
\item \cvitem{}{\textbf{Chen Luo}, Fei He, and Carlo Ghezzi. Inferring Software Behavioral Models 
	with MapReduce. \textit{Science of Computer Programming}, 145 (2017): 13-36
}
}

\clearpage
\end{document}
